Ensemble Super-Learning for State Estimation. \\Application to the reconstruction of urban pollution.

### 2023-09-01 paper/main.tex
Add kernel methods. Add pollution map plotting. Experiments for paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation set-up}
\asmodif{
To validate the results we can only rely on the available (few) sensors (at most $\perplexityinsert{numstations}$) and it does not suffice to make a split of training and testing in time because we observed that models tend to over-fit the locations in which they where trained. For this we need to perform a tripple Leave-One-Out procedure on the stations: one for testing, one for training super-learners and the final one for trainig each individual model.
\begin{enumerate}
	\item \textbf{Test split}: The first split is performed both in time and space. We take the first $\perplexityinsert{percentagetraintime}\%$ of the available times ($\perplexityinsert{numberoftraintimes}$ hours) for training $T_{\train}$ and the rest for testing $T_{\test}$. The Leave-One-Out is done on the station locations $r^\obs$ and associated pollution measurements $z$. As some stations are too near the border of the image, the available traffic information is not enough to add meaningfull information, for this reason even though we use all stations as information, we only take $\perplexityinsert{numstationstest}$\footnote{Stations away from borders are: \perplexityinsert{stationstest}.} for perfoming the testing Leave-One-Out. This means that we have to train in total $\perplexityinsert{numstationstest}$ different set of models associated with the different testing data splits $s\in S$, $\#S=\perplexityinsert{numstationstest}$, $I_s=\{i \in_{i \neq s} \{1, \dots m\}\}$
\begin{align}
	Y^{\test}_s(t) &= (z_s(t), r^\obs_s) \in \bR \times \bR^{2} \, \forall t \in T_{\test} \\
	X^{\train}_s(t) &= (z_{I_s}(t), r^\obs_{I_s}, q, T, w) \in \bR^{m-1} \times \bR^{2(m-1)} \times V \times \bR\times \bR^2 \, \forall t \in T_{\train}.	
\end{align}
	So the test error will be calculated as follws:
	$$e(u,A) \approx e^{\test}_{LOO}(Y^{\test}_s, A) = \frac{1}{\#T_{\test}}\sum_{t\in T_{\test}}\left(z_s-A(X^{\train}_s)(r^\obs_s)\right)^2$$
    \item \textbf{Super-learner train split}: For each training set we perform another Leave-One-Out to train each super-learner $(Y^{SL}_s, X^{SL}_s)$ both in $X^{\train}_s$.
    \item \textbf{Individual models train split}: For each training super-learner set we perform eone more Leave-One-Out to train each individual model under different circumstances avoiding this way the possibility of over-fitting: $(Y^{M}_s, X^{M}_s)$ both in $X^{SL}_s$.
\end{enumerate}
}{}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation set-up}
\asmodif{
To validate the results we can only rely on the available (few) sensors (at most $\perplexityinsert{numstations}$) and it does not suffice to make a split of training and testing in time because we observed that models tend to over-fit the locations in which they where trained. For this we need to perform a tripple Leave-One-Out procedure on the stations: one for testing, one for training super-learners and the final one for trainig each individual model (see \cref{fig:loodiagram} for a schematic view of the successive splitings).
\begin{enumerate}
	\item \textbf{Test split}: The first split is performed both in time and space. We take the first $\perplexityinsert{percentagetraintime}\%$ of the available times ($\perplexityinsert{numberoftraintimes}$ hours) for training $T_{\train}$ and the rest for testing $T_{\test}$. The Leave-One-Out is done on the station locations $r^\obs$ and associated pollution measurements $z$. As some stations are too near the border of the image, the available traffic information is not enough to add meaningfull information, for this reason even though we use all stations as information, we only take $\perplexityinsert{numstationstest}$\footnote{Stations away from borders are: \perplexityinsert{stationstest}.} for perfoming the testing Leave-One-Out. This means that we have to train in total $\perplexityinsert{numstationstest}$ different set of models associated with the different testing data splits $s\in S$, $\#S=\perplexityinsert{numstationstest}$, $I_s=\{i \in_{i \neq s} \{1, \dots m\}\}$
\begin{align}
	Y^{\test}_s(t) &= (z_s(t), r^\obs_s) \in \bR \times \bR^{2} \, \forall t \in T_{\test} \\
	X^{\train}_s(t) &= (z_{I_s}(t), r^\obs_{I_s}, q, T, w) \in \bR^{m-1} \times \bR^{2(m-1)} \times V \times \bR\times \bR^2 \, \forall t \in T_{\train}.	
\end{align}
	So the test error will be calculated as follws:
	$$e(u,A) \approx e^{\test}_{LOO}(Y^{\test}_s, A) = \frac{1}{\#T_{\test}}\sum_{t\in T_{\test}}\left(z_s-A(X^{\train}_s)(r^\obs_s)\right)^2$$
    \item \textbf{Super-learner train split}: For each training set we perform another Leave-One-Out to train each super-learner $(Y^{SL}_s, X^{SL}_s)$ both in $X^{\train}_s$.
    \item \textbf{Individual models train split}: For each training super-learner set we perform eone more Leave-One-Out to train each individual model under different circumstances avoiding this way the possibility of over-fitting: $(Y^{M}_s, X^{M}_s)$ both in $X^{SL}_s$.
\end{enumerate}
}{}
